Adaptive Disk Storage for Interaction Graphs

### 2014-06-24 docs/graph-adapt/main.tex
non-overlapping alg

\author{Bu\u{g}ra Gedik         \and
        Robert Soul\'{e}%etc.
}

@@

\paragraph*{Approach.}

Idea1: Start with each attribute on its own, but as a set. At each step,
consider  merging two existing sets, but pick the pair that results in the 
maximum reduction in query cost per overhead removed.

>>>>

\author{Robert Soul\'{e}         \and
        Bu\u{g}ra Gedik%etc.
}

@@

%$\mathcal{P}(B) \leftarrow \emptyset$ \tcp*{Initial partitioning}

\begin{algorithm}[h]
\scriptsize
\caption{Algorithm for partitioning blocks into sub-blocks with non-overlapping attributes.}
\label{alg:overlappingP}
\KwData{$B$: block, $Q$: set of queries}
$c^*\leftarrow \infty$ \tcp*{Lowest cost over all \# of partitions}
\For(\tcp*[f]{For each possible \# of partitions}){$k=1$ to $|A|$}{
   $R[i]\leftarrow \emptyset, \forall i\in [1..k]$ \tcp*{Initialize partitions}
   \For(\tcp*[f]{For each attribute}){$a \in A$\textnormal{, in decr.\/ order of }$f(a)$}{
      $c\leftarrow \infty$ \tcp*{Lowest cost over all assignments}  
      $j\leftarrow -1$ \tcp*{Best partition assignment}
      \For(\tcp*[f]{For each partition assignment}){$i\in [1..k]$} {
         $R[i]\leftarrow R[i] \cup \{a\}$\tcp*{Assign attribute}
         \If(\tcp*[f]{If size is not feasable}){$H(R, B, Q)\geq\alpha$}{
            \textbf{continue}
         }
         \If(\tcp*[f]{If query cost is lower}){$L(R, B, Q)<c$}{
            $c\leftarrow L(R, B, Q)$\tcp*{Update the lowest cost}
            $j\leftarrow i$\tcp*{Update the best partition}
         }
         $R[i]\leftarrow R[i] \setminus a$\tcp*{Un-assign attribute}
      }
      $R[j]\leftarrow R[j] \cup a$\tcp*{Assign to best partition}
   }
   \If(\tcp*[f]{If query cost is lower}){$L(R, B, Q)<c^*$}{
      $c^* \leftarrow L(R, B, Q)$\tcp*{Update the lowest cost}
      $\mathcal{P}(B)\leftarrow R$\tcp*{Update the best partitioning}
   }
}
\Return $\mathcal{P}(B)$ \tcp*{Final set of sub-blocks}
\end{algorithm}
